### 2017-06-20 manuscript/manuscript.Rmd
Complex sentences are less fun that simple ones.

Neither of these operations---checking out an earlier version of a file or of the entire project---affects the history of the project, and are therefore "safe", in the sense that your project's history won't be overwritten. However, checking out an earlier version of a specific file changes the current state of the project (the current version of the file is temporarily overwritten with the old version), so it is good practice to carefully keep track of the current version of your file before making further commits.

>>>>

Both of these operations---checking out an earlier version of a file or of the entire project---are "safe" in the sense that your project's history won't be affected. However, checking out an earlier version of a specific file changes the current state of the project (the current version of the file is temporarily overwritten with the old version), so it is good practice to carefully keep track of the current version of your file before making further commits.
